### 2021-02-13 evaluation.tex
Explain that we ignore the time to preprocess

@@

\todo{Mention: time to compute graphs and precedences is excluded from the time.}

>>>>

To generate a precedence for a problem,
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit is only imposed on the Vampire run
and excludes the time taken by the recommender to generate the precedence.
\todo{Update if we include the preprocessing time.}

@@
